SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-01 My-Papers/SpecHunter/paper.tex
Outlines and code example

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

@@

@@

%%   Abstract
%%   Note: \begin{abstract}...\end{abstract} environment must come
%%   before \maketitle command
\begin{abstract}
  % Taint analysis becomes a must for Java projects where foreign codes such as
  % external frameworks are frequently used in building them.
  % % Taint specification 추론이 왜 필요한지
  % For accurate taint analysis, the analyzer must first be told which methods are
  % sources, sinks, sanitizers, or none of them. However, Manually determining such
  % labels for every method used or defined in a project is a tedious task that
  % becomes nearly impossible if the codebase becomes large.
  % % 그러므로 우리의 아이디어를 제시한다
  % To alleviate such burden, we present Spechunter which, given a small
  % portion of the entire methods which are not deadcodes, finds out taint specifications
  % of the rest of the methods in a Java project built with frameworks.
  % % 우리 아이디어의 특징
  % Spechunter's uniqueness lies in its efficiency, achieved by only
  % drawing minimum manpower necessary for doing its job. This is possible due to its
  % interactive nature: it ends an ongoing interaction as soon as it determines that enough
  % evidence is obtained from the oracle. To achieve this, Spechunter relies on
  % building Bayesian networks and performing marginal inference on it given accumulating
  % evidence. Our experiments show that ...

  % 위의 버전은 영양가도 없으면서 너무 장황하다. Lets give it a full rewrite!

  SpecHunter is a tool for inferring taint specifications, aiming to serve any
  Java taint analyzers, enabling them to be more precise in finding out data
  flows from a source method to a sink method, without passing through a
  sanitizer. By asking questions to an external oracle on selected APIs used in
  a given Java application, it can acheive the following two goals. First,
  SpecHunter is language-agnostic, since it only focuses on the Java application at
  hand, and ignores whether or not the used APIs are implemented in languages
  other than Java. Therefore, it can be used for any Java application, regardless
  of what libraries or frameworks they use. Second, SpecHunter is
  efficient, because the APIs necessary for efficient propagation is automatically selected
  by SpecHunter itself. This allows the user to skip all trial-and-error in
  configurating the training set for a learning model, as required by previous
  machine learning approaches. Results of our experiments show that SpecHunter
  actually delivers the aforementioned promises, by running on applications with
  Scala and C++ libraries, with only questions asked to the user.  
\end{abstract}

@@

\section{Introduction}
% A large portion of Java projects are built using frameworks such as Spring,
% Hibernate, or Android. These frameworks are foreign codes, so importing their
% APIs may introduce new security vulnerabilities. Finding out such security holes
% requires running taint analysis, which looks for a data flow starting from a
% source method to a sink method without passing through a sanitizer method.
% However, taint analyzers should be correctly told which method is a source,
% sink, sanitizer, or none of them at the first place, otherwise it may result in
% false negatives or false positives. However, manually labelling all methods used
% or defined in a project with the above four labels is a laborous task to be
% manually done, and becomes nearly impossible to do so if the codebase gets
% larger. Therefore, there have been previous works to lessen this burden.

% 2021-02-15 16:44:59에 다시 쓴 버전:

Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
in the given program. These vulnerabilities include SQL injection, cross-site
scripting, and abused printf-arguments. They are typically formulated as a
data flow starting from a `source' method to a `sink' method, without the
flowing data being `sanitized' by an appropriate method. For such search to be
precise enough, the analyzer must first be told which methods are sources,
sinks, sanitizers, or none of them. However, going through the codebase
searching for imported APIs and labelling every one of them by hand becomes too
time-consuming as the codebase gets larger.

@@

\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
such as a support vector machine with the actual library codes implementing
APIs. Here, the function bodies are interprocedurally analyzed with a Java
static analyzer to get the vectors of feature values. Then, they take a whole
library codebase into the pre-trained learning
model, and get the mapping from all APIs in the library to their respective
specifications. While they work nice against libraries written in pure Java
code such as Spring, they cannot work if a given application imports libraries
written in other languages other than Java. This is because in order to extract
the feature values they would have to be equipped with all the possible
languages the libraries would be in, and this is practically difficult.

@@

Our tool, SpecHunter, works in a different manner than data-driven
approaches. Instead of training the model with some predetermined pairs of
methods and their labels to predict other methods' labels, we analyze the given
application to construct probabilistic graphical models of a certain type,
called Bayesian networks. They are special in that they provide a model of
conditional-probabilistic reasoning, which infers the marginal probabilities of
each random variables when some of them are instantiated to a certain value by
an external source. Therefore, we determine a structure of a Bayesian network by
running a static analysis on the given application code, and make the system ask
the user, the external entity, for evidence. Then, SpecHunter picks the most
influential node which has the most other nodes that depend upon it. This makes
the interaction session both effective and efficient.

The experiments show that ...   % TODO

@@

- We provide SpecHunter
- We provide src/sin/san/non ground truths
- We provide a taint analyzer (is it possible?)
- We make the tool open source (is it possible?)

@@

Swan sucks: too much variance on its performance

\paragraph{Overview of our System}

\paragraph{Static Analysis}

\paragraph{Constructing Bayesian Networks}

@@

\paragraph{Discussions}

\paragraph{Limitations}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigconf,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

@@

\usepackage{listing}

@@

%%   Abstract
%%   Note: \begin{abstract}...\end{abstract} environment must come
%%   before \maketitle command
\begin{abstract}
  SpecHunter is a tool for inferring taint specifications, aiming to aid anyone
  trying to use a Java taint analyzer, but being overwhelmed by the number of APIs that
  should be marked of their specifications to run it. SpecHunter aims to lessen this burden
  by constructing a Bayesian network and performing live interaction with the user, in which
  it systematically picks a method and asks the user of its specification. By taking an
  interactive approach, SpecHunter can run on Java applications that use libraries that are
  implemented in languages other than Java. Also, SpecHunter skips all trial-and-errors
  in configurating the data-set required in using any of the traditional machine-learning approaches.
  Our experiments show that SpecHunter actually delivers those promises.
\end{abstract}

@@

\section{Introduction}
Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
in the given program. These vulnerabilities include SQL injection, cross-site
scripting, and abused printf-arguments. They are typically formulated as a
data flow starting from a `source' method to a `sink' method, without the
flowing data being `sanitized' by a relevant method. For such search to be
precise enough, the analyzer must first be told which methods are sources,
sinks, sanitizers, or none of them. However, going through the codebase
searching for imported APIs and labelling every one of them by hand quickly becomes tedious
thing to do as the codebase gets larger.

@@

\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
such as a support vector machine with the actual library codes implementing
APIs. Here, the function bodies are interprocedurally analyzed with a Java
static analyzer to get the vectors of feature values. Then, they take a whole
library codebase into the pre-trained learning
model, and get the mapping from all APIs in the library to their respective
specifications. While they work nicely against libraries written in pure Java
code such as Spring, they cannot work if a given application imports libraries
written in other languages other than Java. This is because in order to extract
the feature values they would have to be equipped with all the possible
languages the libraries would be in, and this is practically difficult.

@@

Our tool, SpecHunter, works in a different manner than data-driven
approaches. Instead of training the model with some predetermined pairs of
methods and their labels to predict other methods' labels, we analyze the given
application to construct probabilistic graphical models of a certain type,
called Bayesian networks. They are special in that they provide a model of
conditional-probabilistic reasoning, which infers the marginal probabilities of
each random variables when some of them are instantiated to a certain value by
an external source. Therefore, we first determine a structure of a Bayesian network
by running a static analysis on the given application code, and make the system ask
the user, the external entity, for evidence. Then, SpecHunter picks the most
influential node which has the most dependent nodes. This makes the interaction
session both effective and efficient.

The experiments show that SpecHunter effectively infers taint specifications for
methods that are untold of its label, with \textbf{xx}\% precision when told only
\textbf{17.7}\% of all APIs.

@@

\begin{itemize}
  \item We provide SpecHunter
  \item We provide src/sin/san/non ground truths
  \item We provide a taint analyzer (is it possible?)
  \item We make the tool open source (is it possible?)
\end{itemize}

@@

Swan sucks: too much variance on its performance depending on dataset quality/quantity

\subsection{Overview of our System}

% 적당한 figure 하나 넣자

Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
source code, SpecHunter labels all API methods provided by the library the application
uses. There are three main issues regarding building an effective interactive system:
namely, constructing the network, effectively propagating the evidence given from the
oracle, and making the system scale to run on large input applications.
% Question: Should we define what "API" means?

\subsection{Network Construction}

% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
Here we describe how we represent the input java project into a graph form, which will
later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
where V is the set of all methods used or defined in the given application, and E is a
subset of V * V, whose elements are gathered in three different ways.

First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
given input application to calculate lifetimes of all access paths found in the entire code.
% 여기서 간단한 예제 넣어주기

\begin{figure}[t]
  \begin{lstlisting}

    public int m1() {
      return 1;
    }

    public int m2(int u1) {
      return ++u1;
    }

    public void m3(int u2) {
      System.out.println(u2);
    }

    public void f() {
      int x = m1();
      g(x);
    }

    public void g(int y) {
      int z = m2(y);
      h(z);
    }

    public void h(int w) {
      m3(w);
    }

  \end{lstlisting}
\caption{Example Java program with a data flow.}
vspace{-0.6em}
\label{fig:sca}
\end{figure}

Second, there are call-edges.

Last but not least, there are similarity-edges.

\subsection{Graph Splitting}

\subsection{Information Propagation}

@@

\subsection{RQs}
\begin{itemize}
  \item How effective is SH in finding src/sin/san?  % I am really really worried about this
  \item How efficient is SH?
  \item Interaction user-study % possible?
\end{itemize}

% why is this meaningful? (with/without comparison)
% at least mention comparison

\paragraph{Discussions}
How well are propagations working? (Quant, Qualit) .
How stable is SpecHunter over multiple iterations?
\paragraph{Limitations}

\paragraph{Threats to Validity.}
